### 2017-01-03 paper/evaluation.tex
Fixed typos and added some reminders

We are interested in understanding the prevalence of time-consuming
test suites and main sources of cost. We want to understand how the
execution cost is distributed on test cases withing a test suite and
how developers approach test execution. Based on that, we study
parallelization of testing frameworks.  More precisely, we investigate
how prevalent test parallelization is, the potential for improving
execution cost, issues of flakiness that hinders use of
parallelization, and how to address those issues.  More specifically,
we pose the following research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often are parallelization features in
build files?}
\newcommand{\RQD}{What is the impact of parallalelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects. The second research question addresses
the balance of regression tests. We want to investigate how the time
cost of a test suite is distributed among test cases. The third
research question addresses our interest in understanding if
developers are aware of parallelization features from testing
frameworks available out-of-the-box through build systems (\eg, run
JUnit test cases in parallel using Maven Surefire) and what setting
are more often used.  The fourth research question addresses the
impact of parallelism on the regression tests from our sample set. For
subjects that use parallelization settings, we are interested in
compare the execution performance when these settings are activated
and deactivated (\ie, sequential execution). The fifth research
question addresses the characteristics of regression tests from the
previous experiment.  More specifically, we want to investigate if
there is a relation between the balance of test execution (\ie, how
uniformly distributed is the execution time across tests cases) and
the usage of computational resources (\ie, if tests are mostly CPU or
IO intense) that impacts the effectiveness of parallelization.
Finally, the sixth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

>>>>

We are interested in understanding the prevalence of time-consuming
test suites and main sources of cost. We want to understand how the
execution cost is distributed on test cases withing a test suite and
how developers approach test execution. Based on that, we study
parallelization of testing frameworks.  More precisely, we investigate
how prevalent test parallelization is, the potential for improving
execution cost, issues of flakiness that hinders the use of
parallelization, and how to address those issues.  More specifically,
we pose the following research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost from a test suite is distributed
among the test cases?}
\newcommand{\RQC}{How often are parallelization features in
build files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
through parallelization?\Jbc{Previously as "When does parallelization
works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects. The second research question addresses
the balance of regression tests: we want to investigate how the time
cost is distributed among test cases. The third
research question addresses our interest in understanding if
developers are aware of parallelization features from testing
frameworks available out-of-the-box through build systems (\eg, run
JUnit test cases in parallel using Maven Surefire) and what settings
are more often used.  The fourth research question addresses the
impact of parallelism on the regression tests from our sample set. For
subjects that use parallelization settings, we are interested in
compare the execution performance when these settings are activated
and deactivated (\ie, sequential execution) to evaluate the benefits.
\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
addresses the characteristics of regression tests from the previous
experiment.  More specifically, we want to investigate if there is a
relation between the balance of test execution (\ie, how uniformly
distributed is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization}.  Finally, the
sixth research question discusses the limitations and insights to
overcome the pitfalls of parallelization.
